% latex.default(i.tex, file = filename, caption = caption, rowname = NULL,      booktabs = TRUE, longtable = TRUE, lines.page = nrow(i.tex),      here = TRUE, col.just = col.just) 
%

\setlongtables


\begin{longtable}{p{70mm}p{10mm}p{10mm}p{10mm}p{10mm}p{10mm}p{10mm}p{10mm}} \caption{Cluster table 1}\tabularnewline
 \toprule
\multicolumn{1}{c}{taxon}&\multicolumn{1}{c}{layer}&\multicolumn{1}{c}{ks07}&\multicolumn{1}{c}{ks01}&\multicolumn{1}{c}{ks02}&\multicolumn{1}{c}{ks10}&\multicolumn{1}{c}{ks04}&\multicolumn{1}{c}{ks12}\tabularnewline
\midrule
\endfirsthead
\caption[]{\em (continued)} \tabularnewline
\midrule
\multicolumn{1}{c}{taxon}&\multicolumn{1}{c}{layer}&\multicolumn{1}{c}{ks07}&\multicolumn{1}{c}{ks01}&\multicolumn{1}{c}{ks02}&\multicolumn{1}{c}{ks10}&\multicolumn{1}{c}{ks04}&\multicolumn{1}{c}{ks12}\tabularnewline
\midrule
\endhead
\midrule
\endfoot
\label{i.tex}
Crepis alpestris&hl&r&.&.&.&.&.\tabularnewline
Asplenium ruta-muraria&hl&+&+&.&.&.&.\tabularnewline
Berberis vulgaris&hl&+&+&.&.&.&.\tabularnewline
Erica carnea&hl&.&+&.&.&.&.\tabularnewline
Leontodon incanus&hl&.&+&.&.&.&.\tabularnewline
Hieracium bifidum&hl&.&+&+&.&.&.\tabularnewline
Larix decidua&hl&.&+&+&.&.&.\tabularnewline
Amelanchier ovalis&hl&1&+&1&+&.&.\tabularnewline
Gypsophila repens&hl&2a&2a&2a&2a&.&.\tabularnewline
Saxifraga paniculata&hl&+&.&+&+&.&.\tabularnewline
Squamarina lamarckii&hl&.&1&1&1&.&.\tabularnewline
Potentilla caulescens subsp. caulescens&hl&.&.&+&.&.&.\tabularnewline
Thymus praecox subsp. polytrichus&hl&+&+&+&.&1&.\tabularnewline
Polygonatum odoratum&hl&+&+&+&+&+&.\tabularnewline
Sedum album&hl&+&+&+&+&+&.\tabularnewline
Rosa subcollina&hl&+&.&.&.&r&.\tabularnewline
Globularia cordifolia s.str.&hl&1&+&2b&1&.&1\tabularnewline
Anthericum ramosum&hl&+&1&1&+&+&1\tabularnewline
Carduus defloratus subsp. viridis&hl&1&+&+&+&+&+\tabularnewline
Carex ornithopoda subsp. ornithopoda&hl&1&+&+&+&+&+\tabularnewline
Clinopodium alpinum subsp. alpinum&hl&+&+&+&+&+&+\tabularnewline
Juniperus sabina&hl&2a&2a&2a&2b&3&4\tabularnewline
Laserpitium latifolium subsp. latifolium&hl&+&+&+&+&+&+\tabularnewline
Sesleria caerulea s.str.&hl&+&1&1&2a&1&2b\tabularnewline
Teucrium montanum&hl&2b&+&+&+&2a&1\tabularnewline
Calamagrostis varia&hl&2b&+&1&.&2a&2b\tabularnewline
Galium anisophyllon&hl&+&+&+&.&+&+\tabularnewline
Polygala chamaebuxus&hl&1&+&+&.&1&1\tabularnewline
Vincetoxicum hirundinaria&hl&1&+&+&.&1&+\tabularnewline
Viola hirta&hl&+&+&+&.&+&+\tabularnewline
Carex alba&hl&2b&2a&.&1&2a&+\tabularnewline
Erysimum sylvestre s.str.&hl&+&r&.&+&+&+\tabularnewline
Allium lusitanicum&hl&1&.&+&1&+&1\tabularnewline
Buphthalmum salicifolium&hl&1&.&+&+&+&2m\tabularnewline
Picea abies&hl&r&+&.&.&+&+\tabularnewline
Helianthemum nummularium subsp. obscurum&hl&+&.&+&.&+&1\tabularnewline
Sorbus aria agg.&hl&+&.&+&.&+&+\tabularnewline
Juniperus communis subsp. communis&hl&.&+&+&.&1&1\tabularnewline
Rosa micrantha&hl&.&+&+&.&+&+\tabularnewline
Poa molinieri&hl&.&1&+&.&.&+\tabularnewline
Origanum vulgare subsp. vulgare&hl&+&.&.&+&.&+\tabularnewline
Aster alpinus&hl&.&+&.&+&.&+\tabularnewline
Mercurialis perennis s.str.&hl&.&+&.&.&+&+\tabularnewline
Silene nutans subsp. nutans&hl&.&+&.&.&+&+\tabularnewline
Hippocrepis comosa&hl&.&.&+&.&+&+\tabularnewline
Echium vulgare subsp. vulgare&hl&+&.&.&.&.&+\tabularnewline
Thesium alpinum&hl&.&+&.&.&.&+\tabularnewline
Rosa tomentosa&hl&.&.&+&.&.&+\tabularnewline
Scabiosa columbaria s.str.&hl&.&.&+&.&.&+\tabularnewline
Leontodon hispidus subsp. pseudocrispus&hl&.&.&.&1&.&+\tabularnewline
Rhamnus cathartica&hl&.&.&.&.&+&+\tabularnewline
Asplenium trichomanes s.lat.&hl&.&.&.&.&.&+\tabularnewline
Campanula trachelium&hl&.&.&.&.&.&+\tabularnewline
Cotoneaster tomentosus&hl&.&.&.&.&.&+\tabularnewline
Fraxinus excelsior&hl&.&.&.&.&.&+\tabularnewline
Galium mollugo s.str.&hl&.&.&.&.&.&+\tabularnewline
Melica nutans s.str.&hl&.&.&.&.&.&+\tabularnewline
Rosa canina&hl&.&.&.&.&.&+\tabularnewline
Valeriana tripteris&hl&.&.&.&.&.&+\tabularnewline
Rosa subcollina&wl&+&.&.&.&.&.\tabularnewline
Larix decidua&wl&1&+&.&2a&.&.\tabularnewline
Populus tremula&wl&.&.&+&.&.&.\tabularnewline
Juniperus communis subsp. communis&wl&1&1&1&2a&2a&2b\tabularnewline
Amelanchier ovalis&wl&.&+&1&2a&.&+\tabularnewline
Picea abies&wl&.&.&.&+&+&+\tabularnewline
Fraxinus excelsior&wl&.&.&.&2a&.&+\tabularnewline
Rosa micrantha&wl&.&.&.&.&1&+\tabularnewline
Cotoneaster tomentosus&wl&.&.&.&.&.&+\tabularnewline
Rosa canina&wl&.&.&.&.&.&1\tabularnewline
Rosa glauca&wl&.&.&.&.&.&1\tabularnewline
\bottomrule
 \end{longtable}
  
