% latex.default(i.tex, file = filename, caption = caption, rowname = NULL,      booktabs = TRUE, longtable = TRUE, lines.page = nrow(i.tex),      here = TRUE, col.just = col.just) 
%

\setlongtables


\begin{longtable}{p{70mm}p{10mm}p{10mm}} \caption{Cluster table 3}\tabularnewline
 \toprule
\multicolumn{1}{c}{taxon}&\multicolumn{1}{c}{layer}&\multicolumn{1}{c}{ks12}\tabularnewline
\midrule
\endfirsthead
\caption[]{\em (continued)} \tabularnewline
\midrule
\multicolumn{1}{c}{taxon}&\multicolumn{1}{c}{layer}&\multicolumn{1}{c}{ks12}\tabularnewline
\midrule
\endhead
\midrule
\endfoot
\label{i.tex}
Allium lusitanicum&hl&1\tabularnewline
Anthericum ramosum&hl&1\tabularnewline
Asplenium trichomanes s.lat.&hl&+\tabularnewline
Aster alpinus&hl&+\tabularnewline
Buphthalmum salicifolium&hl&2m\tabularnewline
Calamagrostis varia&hl&2b\tabularnewline
Campanula trachelium&hl&+\tabularnewline
Carduus defloratus subsp. viridis&hl&+\tabularnewline
Carex alba&hl&+\tabularnewline
Carex ornithopoda subsp. ornithopoda&hl&+\tabularnewline
Clinopodium alpinum subsp. alpinum&hl&+\tabularnewline
Cotoneaster tomentosus&hl&+\tabularnewline
Echium vulgare subsp. vulgare&hl&+\tabularnewline
Erysimum sylvestre s.str.&hl&+\tabularnewline
Fraxinus excelsior&hl&+\tabularnewline
Galium anisophyllon&hl&+\tabularnewline
Galium mollugo s.str.&hl&+\tabularnewline
Globularia cordifolia s.str.&hl&1\tabularnewline
Helianthemum nummularium subsp. obscurum&hl&1\tabularnewline
Hippocrepis comosa&hl&+\tabularnewline
Juniperus communis subsp. communis&hl&1\tabularnewline
Juniperus sabina&hl&4\tabularnewline
Laserpitium latifolium subsp. latifolium&hl&+\tabularnewline
Leontodon hispidus subsp. pseudocrispus&hl&+\tabularnewline
Melica nutans s.str.&hl&+\tabularnewline
Mercurialis perennis s.str.&hl&+\tabularnewline
Origanum vulgare subsp. vulgare&hl&+\tabularnewline
Picea abies&hl&+\tabularnewline
Poa molinieri&hl&+\tabularnewline
Polygala chamaebuxus&hl&1\tabularnewline
Rhamnus cathartica&hl&+\tabularnewline
Rosa canina&hl&+\tabularnewline
Rosa micrantha&hl&+\tabularnewline
Rosa tomentosa&hl&+\tabularnewline
Scabiosa columbaria s.str.&hl&+\tabularnewline
Sesleria caerulea s.str.&hl&2b\tabularnewline
Silene nutans subsp. nutans&hl&+\tabularnewline
Sorbus aria agg.&hl&+\tabularnewline
Teucrium montanum&hl&1\tabularnewline
Thesium alpinum&hl&+\tabularnewline
Valeriana tripteris&hl&+\tabularnewline
Vincetoxicum hirundinaria&hl&+\tabularnewline
Viola hirta&hl&+\tabularnewline
Amelanchier ovalis&wl&+\tabularnewline
Cotoneaster tomentosus&wl&+\tabularnewline
Fraxinus excelsior&wl&+\tabularnewline
Juniperus communis subsp. communis&wl&2b\tabularnewline
Picea abies&wl&+\tabularnewline
Rosa canina&wl&1\tabularnewline
Rosa glauca&wl&1\tabularnewline
Rosa micrantha&wl&+\tabularnewline
\bottomrule
 \end{longtable}
  
