% latex.default(i.tex, file = filename, caption = caption, rowname = NULL,      booktabs = TRUE, longtable = TRUE, lines.page = nrow(i.tex),      here = TRUE, col.just = col.just) 
%

\setlongtables


\begin{longtable}{p{70mm}p{10mm}p{10mm}p{10mm}p{10mm}p{10mm}p{10mm}p{10mm}} \caption{Cluster table 2}\tabularnewline
 \toprule
\multicolumn{1}{c}{taxon}&\multicolumn{1}{c}{layer}&\multicolumn{1}{c}{ks06}&\multicolumn{1}{c}{ks05}&\multicolumn{1}{c}{ks08}&\multicolumn{1}{c}{ks03}&\multicolumn{1}{c}{ks09}&\multicolumn{1}{c}{ks11}\tabularnewline
\midrule
\endfirsthead
\caption[]{\em (continued)} \tabularnewline
\midrule
\multicolumn{1}{c}{taxon}&\multicolumn{1}{c}{layer}&\multicolumn{1}{c}{ks06}&\multicolumn{1}{c}{ks05}&\multicolumn{1}{c}{ks08}&\multicolumn{1}{c}{ks03}&\multicolumn{1}{c}{ks09}&\multicolumn{1}{c}{ks11}\tabularnewline
\midrule
\endhead
\midrule
\endfoot
\label{i.tex}
Leontodon hispidus subsp. pseudocrispus&hl&+&+&.&.&.&.\tabularnewline
Aster alpinus&hl&1&+&+&.&.&.\tabularnewline
Potentilla caulescens subsp. caulescens&hl&+&1&+&.&.&.\tabularnewline
Rhamnus cathartica&hl&+&+&.&+&.&.\tabularnewline
Squamarina lamarckii&hl&1&1&2a&1&.&.\tabularnewline
Hippocrepis comosa&hl&.&+&+&+&1&.\tabularnewline
Galium anisophyllon&hl&+&+&+&+&.&+\tabularnewline
Polygonatum odoratum&hl&+&+&1&+&.&+\tabularnewline
Scabiosa columbaria s.str.&hl&+&+&+&+&.&+\tabularnewline
Polygala chamaebuxus&hl&1&2a&1&.&1&1\tabularnewline
Amelanchier ovalis&hl&+&1&+&+&1&+\tabularnewline
Anthericum ramosum&hl&+&+&+&+&+&1\tabularnewline
Calamagrostis varia&hl&1&1&1&1&2a&2a\tabularnewline
Carex ornithopoda subsp. ornithopoda&hl&+&+&+&1&+&1\tabularnewline
Globularia cordifolia s.str.&hl&2a&2a&2b&2a&+&2a\tabularnewline
Juniperus sabina&hl&2b&2b&2a&2b&4&3\tabularnewline
Laserpitium latifolium subsp. latifolium&hl&+&+&+&+&1&+\tabularnewline
Teucrium montanum&hl&1&2a&1&1&1&1\tabularnewline
Thymus praecox subsp. polytrichus&hl&+&1&+&1&+&+\tabularnewline
Vincetoxicum hirundinaria&hl&+&+&+&1&1&+\tabularnewline
Asplenium ruta-muraria&hl&+&+&.&.&+&+\tabularnewline
Gypsophila repens&hl&+&.&1&2a&1&1\tabularnewline
Juniperus communis subsp. communis&hl&+&.&1&+&1&1\tabularnewline
Berberis vulgaris&hl&.&+&+&.&.&+\tabularnewline
Helianthemum nummularium subsp. obscurum&hl&.&+&1&.&.&+\tabularnewline
Carduus defloratus subsp. viridis&hl&.&+&+&+&.&+\tabularnewline
Rosa micrantha&hl&.&.&.&+&.&.\tabularnewline
Saxifraga paniculata&hl&.&.&.&+&.&.\tabularnewline
Buphthalmum salicifolium&hl&.&+&1&+&2m&1\tabularnewline
Sesleria caerulea s.str.&hl&.&+&+&+&+&2a\tabularnewline
Clinopodium alpinum subsp. alpinum&hl&.&+&+&.&+&1\tabularnewline
Sedum album&hl&.&+&.&+&+&+\tabularnewline
Allium lusitanicum&hl&.&.&1&+&1&1\tabularnewline
Silene nutans subsp. nutans&hl&.&.&+&+&+&+\tabularnewline
Hieracium bifidum&hl&.&.&+&+&.&+\tabularnewline
Erysimum sylvestre s.str.&hl&.&.&+&.&+&+\tabularnewline
Poa molinieri&hl&.&.&.&1&.&+\tabularnewline
Carex digitata&hl&.&.&.&.&.&+\tabularnewline
Galium mollugo s.str.&hl&.&.&.&.&.&+\tabularnewline
Origanum vulgare subsp. vulgare&hl&.&.&.&.&.&+\tabularnewline
Rosa tomentosa&hl&.&.&.&.&.&+\tabularnewline
Thesium alpinum&hl&.&.&.&.&.&+\tabularnewline
Berberis vulgaris&wl&.&1&.&.&.&.\tabularnewline
Amelanchier ovalis&wl&.&2a&2a&1&2a&.\tabularnewline
Corylus avellana&wl&.&.&.&1&.&.\tabularnewline
Rhamnus cathartica&wl&.&+&.&+&2a&+\tabularnewline
Rosa glauca&wl&.&.&.&.&1&.\tabularnewline
Juniperus communis subsp. communis&wl&.&.&.&1&1&2a\tabularnewline
Sorbus aria agg.&wl&.&.&.&+&1&1\tabularnewline
Picea abies&wl&.&.&.&.&.&1\tabularnewline
Rosa canina&wl&.&.&.&.&.&1\tabularnewline
\bottomrule
 \end{longtable}
  
